R Notebook

### 2018-03-30 wiw-study1-nb.Rmd
checked reverse coef

```{r}
library(brms)
fit <- brm(
  response ~ 0 + intercept + (1|workerId) + (1|trial),
  data = d,
  family = bernoulli(), # student(), #cumulative(), #bernoulli(), etc
  control = list(adapt_delta = .80),
  cores = parallel::detectCores(),
  iter = 2000)
```

>>>>

```{r}
library(brms)
fit <- brm(
  response ~ 0 + intercept + likely_2nd + (1|workerId) + (1|trial),
  data = d,
  family = bernoulli(), # student(), #cumulative(), #bernoulli(), etc
  control = list(adapt_delta = .80),
  cores = parallel::detectCores(),
  iter = 2000)
```
